Memory for television episodes preserves event content while introducing new across-event similarities

### 2020-01-06 paper/main.tex
updated embedding section

\subsubsection*{Estimating the consistency of flow through topic space across participants}
In Figure~\ref{fig:trajectory}B, we present an analysis aimed at characterizing locations in topic space that different participants move through in a consistent way (via their recall topic trajectories).  The two-dimensional topic space used in our visualizations (Fig.~\ref{fig:trajectory}) comprised a 9x9 (arbitrary units) square.  We divided this space into a grid of vertices spaced 0.25~units apart.  For each vertex, we examined the set of line segments formed by connecting each pair successively recalled events, across all participants, that passed within 0.5 units.  We computed the distribution of angles formed by those segments and the $x$-axis, and used a Rayleigh test to determine whether the distribution of angles was reliably ``peaked'' (i.e., consistent across all transitions that passed through that local portion of topic space).  To create Figure~\ref{fig:trajectory}B we drew an arrow originating from each grid vertex, pointing in the direction of the average angle formed by line segments that passed within 0.5 units.  We set the arrow lengths to be inversely proportional to the $p$-values of the Rayleigh tests at each vertex.  Specifically, for each vertex we converted all of the angles of segments that passed within 0.5 units to unit vectors, and we set the arrow lengths at each vertex proportional to the length of the (circular) mean vector.  We also indicated any significant results ($p < 0.05$, corrected using the Benjamani-Hochberg procedure) by coloring the arrows in blue (darker blue denotes a lower $p$-value, i.e., a longer mean vector); all tests with $p \geq 0.05$ are displayed in gray and given a lower opacity value.

>>>>

\subsubsection*{Estimating the consistency of flow through topic space across participants}
In Figure~\ref{fig:trajectory}B, we present an analysis aimed at characterizing locations in topic space that different participants move through in a consistent way (via their recall topic trajectories).  The two-dimensional topic space used in our visualizations (Fig.~\ref{fig:trajectory}) comprised a 60 x 60 (arbitrary units) square.  We tiled this space with a 50 x 50 grid of evenly spaced vertices, and defined a circular area centered on each vertex whose radius was two times the distance between adjacent vertices (i.e., 2.4 units).  For each vertex, we examined the set of line segments formed by connecting each pair successively recalled events, across all participants, that passed through this circle.  We computed the distribution of angles formed by those segments and the $x$-axis, and used a Rayleigh test to determine whether the distribution of angles was reliably ``peaked'' (i.e., consistent across all transitions that passed through that local portion of topic space).  To create Figure~\ref{fig:trajectory}B we drew an arrow originating from each grid vertex, pointing in the direction of the average angle formed by line segments that passed within its circular radius.  We set the arrow lengths to be inversely proportional to the $p$-values of the Rayleigh tests at each vertex.  Specifically, for each vertex we converted all of the angles of segments that passed within 2.4 units to unit vectors, and we set the arrow lengths at each vertex proportional to the length of the (circular) mean vector.  We also indicated any significant results ($p < 0.05$, corrected using the Benjamani-Hochberg procedure) by coloring the arrows in blue (darker blue denotes a lower $p$-value, i.e., a longer mean vector); all tests with $p \geq 0.05$ are displayed in gray and given a lower opacity value.
